---
title: "non_parametric_tests"
author: "20122011_thomaskutty"
date: "05/12/2020"
output: pdf_document
---

# Non parametric Tests
## Thomaskutty _ 20122011 - 

Question 1 
signed test ( binomial ) 
QUESTION 1
AIM: To Check if there is a significant difference between pre-test and post-test scores of students.
H0: There is no significant difference between pre-test and post-test scores (p=0.05)
H1: There is a significant difference between pre-test and post-test scores (p!=0.05)
----------------------------------------------------------
```{r}
pre = c(67,71,83,69,68,36,52,72,56,64,76,83,69,68)
post = c(58,62,84,67,72,38,63,72,55,59,76,84,69,72)
df = data.frame(pre,post)
n = length(pre) 
differences = df$pre -df$post
positives = differences>0
L = length(positives[positives == TRUE])
binom.test(L,n,p = 0.5)
```
ans : since p value is higher than alpha we do not reject the null hypotheseis


#  Question 2 

------------------------------------------------
------------------------------------------------------
## Wilcox paired t test
# Aim: To test if there is a significant difference in the employee performance before and after the training.
# H0: There is no significant difference in the employee performance before and after the training(p=0.05).
# H1: There is a significant difference in the employee performance before and after the training(p!=0.05).
--------------------------------------------------------------
```{r}

x = c(61,62,55,62,59,74,62,57,64,62)
y = c(59,63,52,54,59,70,67,65,59,71)
# Create a data frame
wilcox_data_paired <- data.frame( 
    group = rep(c("before", "after"), each = 10),
    weight = c(x,y))
wilcox.test(x,y,
            paired = T)

```

Conclusion: The p-value 1 is greater than 0.05 and we accept the null hypothesis. 
Hence, there is no significant difference in the employee performance before and after the training.


# Question 3                  

run test
H0: two data are randomly selected  
H1: two data are not randomly selected 

-----------------------------------------------------------------
```{r}

library(DescTools)
x <- c("H","T", "T", "H", "H","H","T", "H", "T","T","T","H","H","T","T","T")
RunsTest(x)

```

conclusion : p value is greater than 0.05 so we accept the null
             that the two data are randomly selected 


# Question 4
## Man-Whiteny U test
Aim: To check whether there is a significant difference between the sleep time taken by young age and old age people.
H0: There is no significant difference in the sleep time taken by young and old people(p=0.05).
H1: There is a significant difference in the sleep time taken by young and old people(p!=0.05).

```{r}

young = c(58,42,68,20,15,35,26,40,47,28)
old = c(100,152,147,70,40,95,68,90,112,58)
wilcox.test(young,old)

```

conclusion : the p value is less than 0.05 so we reject the null hypothesis 














